%for a more compact document, add the option openany to avoid
%starting all chapters on odd numbered pages
\documentclass[12pt]{cmuthesis}

% This is a template for a CMU thesis.  It is 18 pages without any content :-)
% The source for this is pulled from a variety of sources and people.
% Here's a partial list of people who may or may have not contributed:
%
%        bnoble   = Brian Noble
%        caruana  = Rich Caruana
%        colohan  = Chris Colohan
%        jab      = Justin Boyan
%        josullvn = Joseph O'Sullivan
%        jrs      = Jonathan Shewchuk
%        kosak    = Corey Kosak
%        mjz      = Matt Zekauskas (mattz@cs)
%        pdinda   = Peter Dinda
%        pfr      = Patrick Riley
%        dkoes = David Koes (me)

% My main contribution is putting everything into a single class files and small
% template since I prefer this to some complicated sprawling directory tree with
% makefiles.

% some useful packages
\usepackage{tikz}
\usepackage{times}
\usepackage{fullpage}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage[numbers,sort]{natbib}
\usepackage{tabularx}
\usepackage{array}
\usepackage[table]{xcolor}
\usepackage{textcomp}
\usepackage{csquotes}
\usepackage{gensymb}
\usepackage[pageanchor=true,plainpages=false, pdfpagelabels, bookmarks,bookmarksnumbered,
%pdfborder=0 0 0,  %removes outlines around hyper links in online display
]{hyperref}
\usepackage{subfig}

\usepackage{pifont}
\newcommand*\colourcheck[1]{%
        \expandafter\newcommand\csname #1check\endcsname{\textcolor{#1}{\ding{52}}}%
}
\newcommand*\colourcross[1]{%
        \expandafter\newcommand\csname #1cross\endcsname{\textcolor{#1}{\ding{53}}}%
}
\newcommand{\ooda}[0]{{\sc OODA}}
\newcommand{\norm}[1]{\left\lVert#1\right\rVert}
\colourcheck{green}
\colourcross{red}

% Approximately 1" margins, more space on binding side
%\usepackage[letterpaper,twoside,vscale=.8,hscale=.75,nomarginpar]{geometry}
%for general printing (not binding)
\usepackage[letterpaper,twoside,vscale=.8,hscale=.75,nomarginpar,hmarginratio=1:1]{geometry}

% Provides a draft mark at the top of the document. 
\draftstamp{\today}{DRAFT}

\begin {document} 
\frontmatter

%initialize page style, so contents come out right (see bot) -mjz
\pagestyle{empty}

\title{ %% {\it \huge Thesis Proposal}\\
{Towards Fully-Autonomous Ultralight Drones}}
\author{Mihir Bala}
\date{April 21, 2025}
\Year{2025}
\trnumber{}

\committee{
Mahadev Satyanarayanan, Chair \\
David O'Hallaron \\
Jeff Schneider \\
Padmanabhan Pillai
}

\support{This material is based upon work supported by the
U.S. Army Research Office and the U.S. Army Futures Command
under Contract No. W519TC-23-C-0003 and by the National Science
Foundation under grant number CNS-2106862. The content of the
information does not necessarily reflect the position or the policy of
the government and no official endorsement should be inferred. This
work was done in the CMU Living Edge Lab, which is supported by
Intel, Arm, Vodafone, Deutsche Telekom, CableLabs, Crown Castle,
InterDigital, Seagate, Microsoft, the VMware University Research
Fund, IAI, and the Conklin Kistler family fund.}
\disclaimer{ Any opinions,
findings, conclusions or recommendations expressed in this document
are those of the author and do not necessarily reflect the view(s) of
their employers or the above funding sources.}

% copyright notice generated automatically from Year and author.
% permission added if \permission{} given.

\keywords{Autonomous Drones, Robotics, Mobile Computing, Edge Computing}

\maketitle

\begin{dedication}
For my dad.
\end{dedication}

\pagestyle{plain} % for toc, was empty

%% Obviously, it's probably a good idea to break the various sections of your thesis
%% into different files and input them into this file...

\begin{abstract}
Autonomous drones have emerged as an exciting new technology which could revolutionize infrastructure inspection, military reconnaissance, and police surveillance. However, the vast majority of today’s platforms are heavy, costly, and difficult to operate. This restricts them from use in many mission settings, such as in densely populated environments, where government regulation forbids autonomous operation of heavy drones near people. Much of this weight comes from the onboard compute resources required for these drones to run the critical computer vision algorithms that provide situational awareness. In this dissertation, I show how autonomy can be induced on lightweight drones using edge computing, offloading high compute jobs to a network-proximal server. I demonstrate how this technique can lead to autonomous aircraft that fly much closer to the FAAs regulatory limits at acceptable performance cost. I also reveal a new operating system designed to unify the disparate landscape of drones under a single, easy-to-program API. I show how this can be leveraged to create heterogeneous collaborative drone swarms on commercial off-the-shelf hardware.\end{abstract}

\begin{acknowledgments}
I would like to thank my family, especially my mom and dad, for their continued support. I'd also like to thank my Pittsburgh friends: Bhavani Iyer, Brian Singer, Clement Fung, Abby Kroon Fung, Trevor Kann, Madeleine Howell Kann, Eric Zeng, Taro Tsuchiya, Joseph Reeves, Archana Iyer, Keane Lucas, Mark Dong, Alejandro Cuevas, and Amelia Cuevas; my college friends: Matthew Qemo, Evan Arora, Matthew Askar, Jack Dolan, Lindsay Tuttle, Alimul Miah, Jagjot Singh, Tony Muscat, James Sabella, Sneh Bhakta, and Kelton Bursch; my DC friends: Alhan Sayyed, Adaah Sayyed, Lavan Rajan, Kiki Sayyed, and Nirmal Maitra; and lastly, my high school friends: Liam Wilson, David Schindler, Patrick Turiano, Grant Keith, and Alex Sutherland. 
\end{acknowledgments}



\tableofcontents
\listoffigures
\listoftables

\mainmatter

%% Double space document for easy review:
%\renewcommand{\baselinestretch}{1.66}\normalsize

% The other requirements Catherine has:
%
%  - avoid large margins.  She wants the thesis to use fewer pages, 
%    especially if it requires colour printing.
%
%  - The thesis should be formatted for double-sided printing.  This
%    means that all chapters, acknowledgements, table of contents, etc.
%    should start on odd numbered (right facing) pages.
%
%  - You need to use the department standard tech report title page.  I
%    have tried to ensure that the title page here conforms to this
%    standard.
%
%  - Use a nice serif font, such as Times Roman.  Sans serif looks bad.
%
% Other than that, just make it look good...

\chapter{Introduction}
\input{intro}
\chapter{Background and Related Work}
\input{chapter2/chapter2}
\chapter{Towards Better Autonomous Drones}
\input{chapter3/chapter3}
\chapter{The SteelEagle Backend}
\input{chapter4/chapter4}
\chapter{A Relay Device with Higher Throughput}
\input{chapter5/chapter5}
\chapter{Benchmarking the SteelEagle Pipeline}
\input{chapter6/chapter6}
\chapter{Drone Agnostic Flight Operations}
\input{chapter7/chapter7}
\chapter{Conclusion and Future Work}
\input{chapter8/chapter8}

%\appendix
%\include{appendix}

\backmatter

%\renewcommand{\baselinestretch}{1.0}\normalsize

% By default \bibsection is \chapter*, but we really want this to show
% up in the table of contents and pdf bookmarks.
\renewcommand{\bibsection}{\chapter{\bibname}}
%\newcommand{\bibpreamble}{This text goes between the ``Bibliography''
%  header and the actual list of references}
\bibliographystyle{plainnat}
\bibliography{thesis} %your bib file

\end{document}